mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-17 Draft3.Rmd
function bodies

As is seen from the output above, the variable `term` is not assigned the result
of the calculation, but an R\ "call" that can eventually be evaluated
[see, e.g., @Wickham2019, for more details on "non-standard evaluation"].

@@

We can include the output in a RMarkdown document by specifying `results='asis'`
in the R code chunk, as has been done below. The R function mathout is just a
wrapper that invokes `mathml(...)` for HTML output and `mathjax(...)` for
LaTeX output.

@@

Thus, the predicate `math/2` could be considered a "macro" that translates a
mathematical element (here, `pbinom(K, N, Pi)`) to a different mathematical
element, namely `fn(..., ...)`.

The low-level predicates `ml/3` and `jax/3` are used to convert mathematical
elements to MathML or LaTeX, respectively.

@@

\pkg{mathml} is an R\ package for pretty mathematical representation of
R\ functions and objects in data analysis, scientific reports and interactive
web content. The features currently supported are listed below, roughly following
the order proposed by [@murrell2000].

>>>>

As is seen from the output above, the variable `term` is not assigned the result
of the calculation, but an R\ "call"
[see, e.g., @Wickham2019, for more details on "non-standard evaluation"]. This
call can eventually be evaluated with `eval(...)`,

@@

We can include the output in a RMarkdown document by specifying `results='asis'`
in the R code chunk, as is done in the next example. The
R\ function `mathout(...)` is just a wrapper that invokes `mathml(...)` for HTML
output and `mathjax(...)` for LaTeX output.

@@

Thus, the predicate `math/2` could be considered a "macro" that translates a
mathematical element (here, `pbinom(K, N, Pi)`) to a different mathematical
element, namely `fn(..., ...)`. The low-level predicates `ml/3` and `jax/3`
convert mathematical elements to MathML or LaTeX, respectively.

@@

\pkg{mathml} is an R\ package for pretty mathematical representation of
R\ functions and objects in data analysis, scientific reports and interactive
web content. The currently supported features are listed below, roughly
following the order proposed by [@murrell2000].
